Place of death in NRS COVID-19 deaths

### 2022-01-13 covid_nrs_place_of_death_visualisations.Rmd
work in progress - distribution of causes of death across places - e.g. cancer deaths distribution between years

>>>>

## Proportion of cause of death by location

This graph shows each of the causes of death divided by place of death - e.g. what proportion of cancer deaths happened at home vs hospital over time?

```{r}
# TODO: proportion of each cause of death that happens in a place

# total_deaths_cause_of_death
(
  current_and_historical_deaths_by_cause_and_location %>%
  ggplot() +
  geom_col(aes(x = place_of_death, fill = place_of_death, y = proportion), alpha = 0.8, colour = "grey10") +
  # geom_segment(aes(x = as.numeric(cause_of_death)-0.45, xend = as.numeric(cause_of_death)+0.45, y = deaths_mean, yend = deaths_mean), size = 0.8, colour = "grey1") +
  # coord_flip() +
  scale_fill_viridis_d() +
  facet_grid(cause_of_death~year) +
  scale_y_continuous(labels = function(x) format(x, big.mark = ",")) +
  theme(
    legend.position = "none", 
    plot.caption = element_text(size = 10, colour = "gray60"),
    legend.title = element_blank(), 
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    ) +
  labs(
    x = NULL,
    y = "Deaths",
    subtitle = paste0(c(paste0("Bars are deaths ",str_remove_all(date_range_text,"Data ")),"Line segments are mean deaths for same period 2015-2019"),collapse="\n")
  ) +
  NULL
)

(
current_and_historical_deaths_by_cause_and_location %>%
  # filter(year!="2020-2021") %>%
  filter(!year %in% c("2020","2021")) %>%
  filter(place_of_death!="Other") %>%
  filter(!cause_of_death %in% c("COVID-19","All")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  mutate(
   cause_of_death = factor(cause_of_death %>% str_wrap(., width = 15), levels = order_of_causes_of_death %>% str_wrap(., width = 15)),  # needed to allow converting to a number for plotting the line segments; str_wrap breaks the text up into lines
   cause_of_death = fct_rev(cause_of_death)
  ) %>%
  ggplot(aes(x = place_of_death, group = year, y = proportion, fill = year)) +
  geom_col(position = position_dodge(width = 0.9)) +
  facet_grid(cause_of_death~.) +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = function(x) scales::percent(x, accuracy = 1)) +
  coord_flip() +
  theme(
    panel.spacing = unit(1, units = "lines"),
    legend.position = "top", legend.title = element_blank()
    ) +
  NULL
)
```
